---
title: "Time Series Analysis"
author: "Shantanu Neema"
output:
  pdf_document: default
  word_document: default
---

\textbf{\large{Solution 1.9}}

The given time series to be checked for weak stationarity is:
$$
x_t = U_{1}sin(2\pi\omega_0t)+U_{2}cos(2\pi\omega_0t)
$$

where $U_1$ and $U_2$ are independent random variables with zero means and $E(U_{1}^2) = E(U_{1}^2) = \sigma^2$ 

Let's check the mean of the function for the stationarity:

$$
\begin{aligned}
\mu_t &= \mathbb{E}[x_t] = \mathbb{E}[U_{1}sin(2\pi\omega_0t)+U_{2}cos(2\pi\omega_0t)]\\
&=sin(2\pi\omega_0t)\mathbb{E}[U_{1}]+cos(2\pi\omega_0t)\mathbb{E}[U_{2}]
\end{aligned}
$$

Since, means of $U_1$ and $U_2$ are zero,

$$
\begin{aligned}
\mu_t &= 0
\end{aligned}
$$

Let's check the autocovariance of the given function:

$$
\begin{aligned}
\gamma_{x}(t,t+h) &= cov(x_t,x_{t+h}) \\
&= cov(U_{1}sin(2\pi\omega_0t)+U_{2}cos(2\pi\omega_0t),U_{1}sin(2\pi\omega_0(t+h))+U_{2}cos(2\pi\omega_0(t+h)))\\
&= sin(2\pi\omega_0t)sin(2\pi\omega_0(t+h))cov(U_1,U_1) + cos(2\pi\omega_0t)cos(2\pi\omega_0(t+h))cov(U_2,U_2)\\
&+ sin(2\pi\omega_0t)cos(2\pi\omega_0(t+h))cov(U_1,U_2) + cos(2\pi\omega_0t)sin(2\pi\omega_0(t+h))cov(U_2,U_1)\\
\end{aligned}
$$
where, $cov(U_1,U_2) = cov(U_2,U_1) = 0$; and $cov(U_1,U_1) = cov(U_2,U_2) = \sigma^2$
$$
\begin{aligned}
\gamma_{x}(t,t+h) &= \sigma^2[sin(2\pi\omega_0t)sin(2\pi\omega_0(t+h)) + cos(2\pi\omega_0t)cos(2\pi\omega_0(t+h))] \\
&= \sigma^2[cos(2\pi\omega_0(t+h)-2\pi\omega_0t)] \\
&= \sigma^2cos(2\pi\omega_0h)
\end{aligned}
$$
Above results suggest the following:
\begin{enumerate}
\item The mean value $\mu_t$ of the given function constant (= 0) and is independent of the time
\item The autocovariance function $\gamma(s,t)$ is independent of time and depends only on the difference of |s - t| (i.e. the lag h)
\end{enumerate}

Above 2 criteria suggest that the given series is \textbf{weakly stationary} type time series and the autocovariance function is given by $\sigma^2cos(2\pi\omega_0h)$

\newpage
## Simulation 

Below are the definition of terms U1 & U2. It is known that U1 & U2 are independent random variables with mean = 0 and  sd = sigma

For sd = 1,

```{r}
sig <- 1
U1 <- rnorm(1,0,sig)
U2 <- rnorm(1,0,sig)
```

Choose sample size n=50 and gradually increase the sample size n from 50 to 5000. Define omega as less than 1/2 keeping denominator a multiple of 2 to ensure completion of at least 1 cycle. 

```{r}
omg <- 1/20
sig <- 1
U1 <- rnorm(1,0,sig) 
U2 <- rnorm(1,0,sig)
N <- c(50,250,1000,5000)
par(mfrow=c(2,2),mar=c(1,1,2,1)+0.1)
count <- 1
for (I in N) {
  t <- 0:I
  
  Xt <- U1*sin(2*pi*omg*t) + U2*cos(2*pi*omg*t)
  
  # Plot the acf function
  ACF_Xt <- acf(Xt,lag.max=50,main="")
  mtext(paste("Sample Size:",I))
  Calc_ACF <- acf(Xt,plot=FALSE,lag.max=51)$acf
  
  # True Results
  True_ACF <- (sig^2)*cos(2*pi*omg*(0:I))
  lines(0:I,True_ACF,col='blue')
}
par(mfrow=c(1,1))
``` 

From above plots, it can be concluded that the larger the sample size the closer to the true Autocorrelation function.
